---
title: "TimeSeries_AirPassengers"
output:
  pdf_document:
    latex_engine: xelatex
---



```{r}
## Main Source and inspiration == http://www.maths.adelaide.edu.au/emac2009/
#Introductory Time Series with R
#by Paul S.P. Cowpertwait and Andrew Viggo Metcalfe
#Springer. ISBN: 978-0-387-88697-8
# All Text below within the QUOTE and UNQUOTE blocks is from this SPRINGER text mentioned above 

library(ggfortify)
library(tseries)
library(forecast)
data(AirPassengers)
ts_AirPassengers <- AirPassengers
class(ts_AirPassengers);head(ts_AirPassengers);tail(ts_AirPassengers);dim(ts_AirPassengers)
# Dimensions = NULL ??
# Check for Missing or NA 
sum(is.na(ts_AirPassengers)) # No Missing values - No NA 
# 

```

Check Frequency of TimeSeries and the Cyclic part of the TS  
Check the summary of TS data  
Plot Raw TimeSeries using the inbuilt base PLOT  
...  
    ...  
    

```{r}

frequency(ts_AirPassengers);cycle(ts_AirPassengers)

summary(ts_AirPassengers)

plot(ts_AirPassengers,xlab="Months", ylab = "Air Passengers RAW Data",
     main=("data(AirPassengers) Raw Data TimeSries Plot"))
```

#QUOTE -- A systematic change in a time series that does not apppear to be PERIODIC  
is known as a TREND -- UNQUOTE

```{r}

```


Seasonality Plot − Air Passengers  

```{r}


boxplot(ts_AirPassengers~cycle(ts_AirPassengers),xlab="Months", ylab = "Air Passengers Count " ,
        main ="Seasonality Plot - Air Passengers ")

```

A repeating pattern within each year is known as a - Seasonal Variation , or seasonality .   
This is true even if the period is not a year - seasonality can be within a time span of a month also.   
   
   QUOTE - Random or stochastic trends are common in Financial TimeSeries -    
   thus Regression model is not appropriate for Fin TS . Further forecating is based   
   on extrapolation (assumption that existing trends will continue )   
   Also in absence of external shock - the linear trend can be easily extrapolated.  
   Outliers are to be managed - robust methods of fitting models and imputation  
   of missing values may be used .- UNQUOTE       
   
   
     
     
     For imputation refer here = https://www.kaggle.com/rohitdhankar/multiple-imputation-of-missing-values   
     Package MICE - Multiple Imputation with MCA  
       Source URL's http://juliejosse.com/wp-content/uploads/2016/06/user2016.pdf  
       https://arxiv.org/pdf/1606.05333v2.pdf  
       
http://www.ats.ucla.edu/stat/r/faq/R_pmm_mi.htm
     
     
       
       
      
      
   
   
   
   
```{r}


```

